\documentclass[10pt]{moderncv}
\moderncvtheme{classic}
\moderncvcolor{black}

\setlength{\makecvheadnamewidth}{10cm}

% space between dates and the text
\setlength{\separatorcolumnwidth}{0.025\textwidth}

%\setlength{\listitemsymbolspace}{5pt}

% Expand a little bit for more space
\usepackage[scale=0.95, top=0.5cm, bottom=0.5cm]{geometry}

\firstname{Alfonso}
\lastname{Ros}
\title{Curriculum Vitae}

\mobile{+49 173 6523397}
\email{alfonso.ros.88@gmail.com}
\social[linkedin][www.linkedin.com/in/alfonsorosdossantos]{Alfonso Ros Dos Santos}
\social[github][https://github.com/rosds]{rosds}
\address{Plinganserstr. 7A}{81369 M\"unchen}

\begin{document}

\maketitle
\vspace*{-1cm}

\section{Summary}

A friendly and dedicated software developer with over 6 years in the German automotive industry, specializing in
high-performance middleware for automotive applications. Currently working on Apex.Ida, a general-purpose middleware with a
strong automotive focus and ROS compatible. Previously, as part of the platform team at Autonomous Intelligent Driving GmbH,
contributed to the development of  a middleware for autonomous driving vehicles. With a strong interest in system-level software
development, brings expertise in C/C++, Rust focusing on concurrency, performance and embedded systems.

\section{Work Experience}

\cventry{June 2022 - present}{Senior Software Engineer}
{\textsc{Apex.AI GmbH}}{Germany}{}{%
\begin{itemize}
    \item Part of Apex.Ida middleware team of about 10 persons, mainly responsible for the support of SOME/IP and CAN transport.
        (vsomeip, cantools, C++17)
    \item Implementation of the internal integration testing framework. (Docker, Bazel, Boost.Asio, libssh2)
    \item Supporting clients on porting their ROS applications to Apex.OS.
\end{itemize}
}

\cventry{2020 - 2022}{Software Engineer}
{\textsc{ESR Labs GmbH}}{Germany}{}{%
\begin{itemize}
    \item Contribution to \href{https://github.com/esrlabs/northstar}{Northstar}, an open-source container runtime written in
        Rust. (POSIX, Cgroups, Tokio)
    \item Responsible for the design and implementation the Intrusion Detection System, an embedded Linux application reacting
        to concurrent signals (Android's messaging and concurrency, Rust).
\end{itemize}
}

\cventry{2019 - 2020}{Software Engineer}
{\textsc{Autonomous Intelligent Driving GmbH}}{Germany}{}{%
\begin{itemize}
  \item Part of the Software Platform Team, a group of about 9 persons dedicated to the development of Fusion, a Vehicle
      Middleware inspired in Qt.
  \item Mainly contributed to the implementation of object method calls and object interface synchronization. (C++11, rti's DDS)
\end{itemize}
}

\cventry{2018 -- 2019}{Project Engineer}
{\textsc{TTTech Auto AG}}{Germany}{}{%
\begin{itemize}
  \item Worked in a self-organized team of 10 persons supporting BMW's Autonomous Driving Project.
  \item Negotiation and plannification of units of work for every sprint (LeSS)
  \item mostly contributing to the implementation of the \textit{Keep Lane Assistant} (C++14, ROS).
\end{itemize}
}

\cventry{2016 -- 2018}{Software Engineer}
{\textsc{evosoft GmbH}}{Germany}{}{%
\begin{itemize}
  \item Part of small team of 5 persons, responsible to implement a real-time monitoring system for electrical substations
      (C/C++, DPDK, RTLinux).
  \item Setup of Continuous Integration and Testing for different micro controllers (Yocto-Linux, LAVA, Python, Go)
\end{itemize}
}

\cventry{2015 -- 2016}{Working Student}
{\textsc{Siemens Corporate Technology}}{Germany}{}{%
\begin{itemize}
  \item Implementation embedded engine for semantic information processing of \textit{Internet of Things} descriptions. (C/C++,
      Cortex-M4, CoAP).
\end{itemize}
}

\cventry{2012 -- 2013}{Software Engineer}
{\textsc{talPor Solutions C.A.}}{Venezuela}{}{%
\begin{itemize}
  \item Web Development using Python (Django).
\end{itemize}
}

\cventry{2008 -- 2011}{System Administrator} {Universidad Sim\'{o}n Bol\'{i}var}{Venezuela}{}{%
\begin{itemize}
  \item Network and System administration (DHCP, DNS, E-Mail, NFS, LDAP).
  \item Teaching Linux and C Programming courses.
\end{itemize}
}

\section{Technical skills}

\cvitem{Languages}{%
\textsc{C/C++17}, Rust, Python
}

\cvitem{Software}{%
  Git, Bazel, CMake, GDB, Linux, Neovim
}

\section{Education}

\cventry{2013--2016}{M.Sc. Informatics}
  {Technische Universit\"at M\"unchen}{Germany}{}{%
    Major: Computer Vision and Machine Learning.
  }

\cventry{2006--2012}{B.S. Computer Science and Engineering}
  {Universidad Sim\'on Bol\'{\i}var}{Venezuela}{}{%
    Award: 2011's Best Computer Science thesis -- IEEE \& Inelectra Venezuela.
  }


\section{Languages}

\cvitem{Spanish}{Mother tongue}
\cvitem{English}{Professional working proficiency}
\cvitem{German}{Intermediate proficiency}

\section{Hobbies}
\cvitem{}{playing Video and Board games, Coffee, painting and a bit of piano playing}

\end{document}
