%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Alfonso Ros} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Jochbergweg 1} % Your address
\moveleft.5\hoffset\centerline{85748, Garching by Munich}
\moveleft.5\hoffset\centerline{+49 173 6523397}
\moveleft.5\hoffset\centerline{alfonsoros88@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelor of Computer Science} \\
Universidad Sim\'on Bol\'ivar, Caracas, Venezuela, 2006-2012\\
Concentration: Machine Learning and Computer Graphics \\
Award: Best Computer Science thesis of the year 2011 - IEEE \& Inelectra Venezuela.
 
{\sl M.Sc. Informatics} \\
Technische Universit\"at M\"unchen, Germany, 2013-present\\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Research Programmer} \hfill 2015-present \\
Siemens CT

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Development and embedded programing of interfaces over the CoAP RESTful 
    environment inside the subject of the Internet of Things.
\end{itemize}

{\sl Web Developer} \hfill 2012-2013 \\
talPor Solutions C.A.

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Back-end and Front-end development of Pollito Ingl\'es. An E-commerce 
    platform for baby care products and children.
\item Back-end and Front-end development of Tunes Alive. An E-commerce platform
    for the distribution and promotion of new music bands.
\end{itemize}
 
{\sl System Administrator} \hfill 2010-2011 \\
Database research group laboratory, Universidad Sim\'on Bol\'ivar
\begin{itemize} 
\item Administration of the laboratory's network and computers.
\item Database administration.
\end{itemize} 

{\sl System Administrator} \hfill 2008-2011 \\
Laboratorio Docente de Computaci\'on, Universidad Sim\'on Bol\'ivar
\begin{itemize} 
\item Administration of the computer network of the informatics faculty.
\item Administration of multiple operating systems and computer architectures.
\item Administration of network services.
\item Teaching for new laboratory members.
\end{itemize} 


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNICAL \\ SKILLS} 

{\sl Languages:} \\
\begin{itemize} 
\item Proficient: C/C++, CUDA and Python
\item Familiar: Matlab, Java, Bash, Javascript, Ruby and Haskell
\end{itemize} 

{\sl Libraries:} \\
\begin{itemize} 
\item Proficient: Point Cloud Library, OpenCV, OpenMPI and OpenMP
\item Familiar: Eigen, libfreenect, OpenNI.
\end{itemize} 

{\sl Operating Systems:} \\
\begin{itemize} 
\item Proficient: Debian and CentosOS.
\item Familiar: Solaris 10, FreeBSD and Windows.
\end{itemize} 
 
{\sl Frameworks and Software:} \\
\begin{itemize} 
\item Familiar: Django, Android, Maya, After Effects, OpenLDAP, BIND (DNS), NFS, Postfix, CUPS, 
    NTP, Apache, PostgreSQL, Oracle and MySQL.
\end{itemize} 

%----------------------------------------------------------------------------------------
%   Languages
%---------------------------------------------------------------------------------------- 

\section{LANGUAGES}

\begin{itemize} 
\item Spanish (Mother tongue)
\item English (Professional working proficiency)
\item German (Elementary proficiency)
\end{itemize} 

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Playing piano, Aquarelle painting, Playing tennis and playing video games.

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
